---
title: "如何绘制带有显著性标记的箱线图/柱状图"
categories:
  - R
  - Visualization
tags:
  - R
  - ggplot
  - p-value
date: '2020-11-26 11:26:00'
updated: '2020-11-26 23:00:00'
---

介绍如何用R绘制多组比较的箱线图/柱状图。
<!-- more -->

## 数据准备

Prerequisites
Make sure you have installed the following R packages:
tidyverse for data manipulation and visualization
ggpubr for creating easily publication ready plots
rstatix provides pipe-friendly R functions for easy statistical analyses.

```{r}
library(ggpubr)
library(rstatix)
# Transform `dose` into factor variable 
df <- ToothGrowth 
df$dose <- as.factor(df$dose) 
# Add a random grouping variable 
df$group <- factor(rep(c("grp1", "grp2"), 30)) 
head(df, 3)
```



## 每个panel中包含两组数据

### 使用一个变量进行分面

Statistical tests
使用dose变量进行分面，并在x轴上水平上比较supp变量。
```{r}
stat.test <- df %>%
  group_by(dose) %>%
  t_test(len ~ supp) %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance()
stat.test
```

Box plots
```{r}
# Create a box plot
bxp <- ggboxplot(
  df, x = "supp", y = "len", fill = "#00AFBB", 
  facet.by = "dose"
  )

# Make facet and add p-values
stat.test <- stat.test %>% add_xy_position(x = "supp")
bxp + stat_pvalue_manual(stat.test)
```

Box plots 显示P值
使分面比例自由，并添加散点Make the facet scale free and add jitter points
使用 `bracket.nudge.y`将括号位置向下调整
不显示ns (non-significant)
显示矫正之后并且Pvalue显著的标志
在p-value标签和plot边框之间添加10%的空格
```{r}
bxp <- ggboxplot(
  df, x = "supp", y = "len", fill = "#00AFBB", 
  facet.by = "dose", scales = "free", add = "jitter"
  )
bxp +  
  stat_pvalue_manual(
    stat.test, bracket.nudge.y = -2, hide.ns = TRUE,
    label = "{p.adj}{p.adj.signif}"
    ) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))
```

Bar plots
使用 add = "mean_sd"用于创建error bar(mean +/- SD)。
需要使用汇总统计函数来自动计算p-value标签位置 add_xy_position()。
```{r}
# Create a bar plot with error bars (mean +/- sd)
bp <- ggbarplot(
  df, x = "supp", y = "len", add = "mean_sd", 
  fill = "#00AFBB", facet.by = "dose"
  )

# Add p-values onto the bar plots
stat.test <- stat.test %>% add_xy_position(fun = "mean_sd", x = "supp")
bp + stat_pvalue_manual(stat.test)
```

Bar plots with jitter points
在计算p-value标签的位置时，需要设定fun = "max"，
从而将括号将从数据点的最大值开始，避免数据点和括号之间的重叠。
```{r}
# Create a bar plot with error bars (mean +/- sd)
bp <- ggbarplot(
  df, x = "supp", y = "len", add = c("mean_sd", "jitter"), 
  fill = "#00AFBB", facet.by = "dose"
  )

# Add p-values onto the bar plots
stat.test <- stat.test %>% add_xy_position(fun = "max", x = "supp")
bp + stat_pvalue_manual(stat.test)
```


###  使用两个变量进行分面
使用dose和group变量进行分面，并在x轴上水平上比较supp变量。

Statistical tests
```{r}
stat.test <- df %>%
  group_by(group, dose) %>%
  t_test(len ~ supp) %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance()
stat.test 
```

Box plots
```{r}
# Create box plots with significance levels
# Hide ns (non-significant)
stat.test <- stat.test %>% add_xy_position(x = "supp")
ggboxplot(
  df, x = "supp", y = "len", fill = "#E7B800",
  facet = c("group", "dose")
  ) +
  stat_pvalue_manual(stat.test, hide.ns = TRUE)
```

Bar plots
```{r}
# Create bar plots with significance levels
# Hide ns (non-significant)
stat.test <- stat.test %>% add_xy_position(x = "supp", fun = "mean_sd")
ggbarplot(
  df, x = "supp", y = "len", fill = "#E7B800",
  add = c("mean_sd", "jitter"), facet = c("group", "dose")
  ) +
  stat_pvalue_manual(stat.test, hide.ns = TRUE)
```
## 每个panel中包含三组或以上的数据

### 使用一个变量进行分面

#### 执行所有两两比较
使用supp变量进行分组，然后对dose变量之间的水平进行两两比较。
Statistical test:
```{r}
stat.test <- df %>%
  group_by(supp) %>%
  t_test(len ~ dose)
stat.test
```

在图中添加p值。
ggplot2中scale_y_continuous(expand = expand (mult = c(0,0.1))用于在标签和图形顶部边框之间添加更多空格
```{r}
# Box plots with p-values
stat.test <- stat.test %>% add_y_position()
ggboxplot(df, x = "dose", y = "len", fill = "#FC4E07", facet.by = "supp") +
  stat_pvalue_manual(stat.test, label = "p.adj.signif", tip.length = 0.01) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))
```

```{r}
# Bar plot with p-values
# Add 10% space on the y-axis above the box plots
stat.test <- stat.test %>% add_y_position(fun = "mean_sd")
ggbarplot(
  df, x = "dose", y = "len", fill = "#FC4E07",
  add = "mean_sd", facet.by = "supp"
  ) + 
  stat_pvalue_manual(stat.test,  label = "p.adj.signif", tip.length = 0.01) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))
```

#### 与参照组进行两两比较
Statistical test:
```{r}
stat.test <- df %>%
  group_by(supp) %>%
  t_test(len ~ dose, ref.group = "0.5")
stat.test
```

Box plots 
```{r}
stat.test <- stat.test %>% add_y_position()
ggboxplot(df, x = "dose", y = "len", fill = "#FC4E07", facet.by = "supp") +
  stat_pvalue_manual(stat.test, label = "p.adj.signif", tip.length = 0.01) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))
```

```{r}
# Show only significance levels at x = group2
# Move down significance symbols using vjust
stat.test <- stat.test %>% add_y_position()
ggboxplot(df, x = "dose", y = "len", fill = "#FC4E07", facet.by = "supp") +
  stat_pvalue_manual(stat.test, label = "p.adj.signif", x = "group2", vjust = 2) 
```

Bar plot
```{r}
# Add 10% space on the y-axis above the box plots
stat.test <- stat.test %>% add_y_position(fun = "mean_sd")
ggbarplot(
  df, x = "dose", y = "len", fill = "#FC4E07",
  add = c("mean_sd", "jitter"), facet.by = "supp"
  ) + 
  stat_pvalue_manual(stat.test,  label = "p.adj.signif", tip.length = 0.01) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))
```

### 使用两个变量进行分面
Statistical test
使用dose和group变量进行分面，并在x轴上水平上比较supp变量。
```{r}
stat.test <- df %>%
  group_by(group, supp) %>%
  t_test(len ~ dose) %>%
  adjust_pvalue(method = "bonferroni") %>%
  add_significance()
stat.test 
```

Box plots
```{r}
# Create box plots with significance levels
# Hide ns (non-significant)
# Add 15% space between labels and the plot top border
stat.test <- stat.test %>% add_xy_position(x = "dose")
ggboxplot(
  df, x = "dose", y = "len", fill = "#FC4E07",
  facet = c("group", "supp")
  ) +
  stat_pvalue_manual(stat.test, hide.ns = TRUE) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
```

Bar plots
```{r}
# Create bar plots with significance levels
# Hide ns (non-significant)
# Add 15% space between labels and the plot top border
stat.test <- stat.test %>% add_xy_position(x = "dose", fun = "mean_sd")
ggbarplot(
  df, x = "dose", y = "len", fill = "#FC4E07",
  add = c("mean_sd", "jitter"), facet = c("group", "supp")
  ) +
  stat_pvalue_manual(stat.test, hide.ns = TRUE) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
```

### 使用group变量进行分面
简单的plot
```{r}
# Box plots
bxp <- ggboxplot(
  df, x = "supp", y = "len", color = "dose", 
   palette = "jco", facet.by = "group"
  )
bxp 
```

Bar plots
```{r}
bp <- ggbarplot(
  df, x = "supp", y = "len", color = "dose",
  palette = "jco", add = "mean_sd",
  position = position_dodge(0.8),
  facet.by = "group"
  )
bp
```

#### 执行所有两两比较
Statistical test:
```{r}
stat.test <- df %>%
  group_by(supp, group) %>%
  t_test(len ~ dose) 
stat.test
```

在图上添加p值:
```{r}
# Box plots with p-values
# Hide ns (non-significant)
stat.test <- stat.test %>%
  add_xy_position(x = "supp", dodge = 0.8)
bxp + 
  stat_pvalue_manual(
    stat.test, label = "p.adj.signif", tip.length = 0.01,
    hide.ns = TRUE
    ) +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0.1)))
```

Bar plots 
```{r}
stat.test <- stat.test %>%
  add_xy_position(x = "supp", fun = "mean_sd", dodge = 0.8)
bp + 
  stat_pvalue_manual(
    stat.test, label = "p.adj.signif", tip.length = 0.01,
    hide.ns = TRUE
    ) +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0.1)))
```

#### 与参照组进行两两比较

Statistical test:
```{r}
stat.test <- df %>%
  group_by(supp, group) %>%
  t_test(len ~ dose, ref.group = "0.5")
stat.test
```

Box plots with p-values
```{r}
stat.test <- stat.test %>%
  add_xy_position(x = "supp", dodge = 0.8)
bxp + 
  stat_pvalue_manual(
    stat.test, label = "p.adj.signif", tip.length = 0.01
    ) +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0.1)))
```

Bar plots with p-values
```{r}
stat.test <- stat.test %>%
  add_xy_position(x = "supp", fun = "mean_sd", dodge = 0.8)
bp + 
  stat_pvalue_manual(
    stat.test, label = "p.adj.signif", tip.length = 0.01
    ) +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0.1)))
```

## version
```{r}
sessionInfo()
getwd()
```

更多相关问题，请参考 [ggpubr FAQ](https://www.datanovia.com/en/blog/tag/ggpubr/)
## 参考链接
[HOW TO ADD P-VALUES TO GGPLOT FACETS](https://www.datanovia.com/en/blog/how-to-add-p-values-to-ggplot-facets/)

参考文章如引起任何侵权问题，可以与我[联系](liaoshuilin@outlook.com)，谢谢。
